---
title: "Example Code"
author: "Zoe Dellaert"
date: "02/20/2020"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE,tidy=TRUE)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lsmeans)
library(mosaic)
library(quantmod)
library(lattice)
library(grid)
library(lindia)
```

## Workflow for extracting surface profiles:

- Drag all images into Fiji
- Make Images —> Stack
- Crop bottom bar out (which automatically crops it out of the whole stack)
- Process > Enhance Contrast (.3%, check all 4 boxes)
- Unfortunately, scale has to be set for each image manually. To do this, I use the pixel length data from the uncropped image 
- Analyze > Set Scale (Distance in pixels = 1, known distance = # from image, unit = nm)
- Draw a line segment perpendicular to spine axis of ~2500nm
- Press Command+b to set this in place
- Drag the line segment down the spine and repeat, ending w/ 10 segments
- Image > Overlay > To ROI Manager
- In the ROI Manager window, with no segments selected (click Deselect), go to More >> Multi Plot
- Save surface profile coordinates as imagename.csv in appropriate folder.

# Example code: Roughness measurements
Shown below is an example of the code that I use in order to extract roughness values from the surface profiles of the images.
```{r,eval=FALSE}
AC_Polyps <- c("AC1a_a","AC1b_a","AC1b_b","AC1b_c","AC2_a","AC2_b")

for (i in AC_Polyps) {
  setwd(paste("~/Rdirectorycoral/Profiles Aug21 - Normalized/AC/",i,sep=""))
  assign(paste("roughness", i, sep = ""), sapply(lapply(list.files(full.names=TRUE,recursive = TRUE),
                                                        function(i){ts(read.csv(i)$Y)}), function(i){roughness(i,std = FALSE)}))
  assign(paste("image_names",i,sep=""), list.files())
  }

#by image
AC_images_vector <- unlist(lapply(AC_Polyps, function(i){paste("image_names",i,sep="")}))
AC_images <- unlist(lapply(AC_images_vector,function(s) eval(parse(text=s))))
roughnessAC_lines_Aug30_images <- unlist(lapply(AC_images,function(i){rep(i,10)}))

for (i in AC_images) {
  name <- paste("~/Rdirectorycoral/Profiles Aug21 - Normalized-image/AC/",i,sep="")
  setwd(name)
  assign(paste("Iroughness", i, sep = ""), sapply(lapply(list.files(full.names=TRUE,recursive = TRUE),
                                                         function(i){ts(read.csv(i)$Y)}), function(i){roughness(i,std = FALSE)}))}

roughnessAC_image_names_Aug30 <- sapply(AC_images, function(i){paste("Iroughness", i, sep = "")}, USE.NAMES = FALSE) 

IroughnessAC_Aug30 <- unlist(lapply(roughnessAC_image_names_Aug30,
                                    function(s) mean(eval(parse(text=s)))))
IroughnessAC_sd_Aug30 <- unlist(lapply(roughnessAC_image_names_Aug30,
                                       function(s) sd(eval(parse(text=s)))))
IroughnessAC_se_Aug30 <- unlist(lapply(roughnessAC_image_names_Aug30,
                                       function(s) sd(eval(parse(text=s)))/sqrt(length(eval(parse(text=s))))))
```

By using this process on my entire data set of 133 images, I am able to create a data table such as shown below. 

```{r,eval=FALSE}
RoughnessDF_byImage <- data.frame("Treatment" = c(rep("15º Aposymbiotic",20),rep("15º Symbiotic",28),rep("27º Aposymbiotic",25),
                                 rep("27º Symbiotic",19), rep("Amb. Aposymbiotic",19),rep("Amb. Symbiotic",22)),
                 "Temp" = c(rep("15º",48),rep("27º",44),rep("20º",19+22)),
                 "Group" = c(rep("Aposymbiotic",20),rep("Symbiotic",28),rep("Aposymbiotic",25),
                             rep("Symbiotic",19),rep("Aposymbiotic",19),rep("Symbiotic",22)), 
                 "Names" = c(AC_images,SC_images,AH_images,SH_images,AW_images,SW_images), 
                 "Roughness" = c(IroughnessAC_Aug30,IroughnessSC_Aug30,IroughnessAH_Aug30,
                                 IroughnessSH_Aug30,IroughnessAW_Aug30,IroughnessSW_Aug30), 
                 "SD" = c(IroughnessAC_sd_Aug30,IroughnessSC_sd_Aug30,IroughnessAH_sd_Aug30,
                          IroughnessSH_sd_Aug30,IroughnessAW_sd_Aug30,IroughnessSW_sd_Aug30),
                 "SE" = c(IroughnessAC_se_Aug30,IroughnessSC_se_Aug30,IroughnessAH_se_Aug30,
                          IroughnessSH_se_Aug30,IroughnessAW_se_Aug30,IroughnessSW_se_Aug30),
                 "Roughness_Log" = c(IroughnessAC_Aug30_LOG,IroughnessSC_Aug30_LOG,IroughnessAH_Aug30_LOG,
                                     IroughnessSH_Aug30_LOG,IroughnessAW_Aug30_LOG, IroughnessSW_Aug30_LOG))
```

```{r}
RoughnessDF_byImage <- read_csv("RoughnessDF_byImage.csv")
head(RoughnessDF_byImage)
```

